---
output: github_document
---


```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(tidyverse)
```

# Dataset: 2019 Argentine General Election

The resulting dataset is availabel in `csv` (for excel) and `RDS` (for R) formats:

- `arg_elec_censo_wide.csv`
- `arg_elec_censo_wide.RDS`

This project aims to create a dataset combining census statistics and electoral results. These are the data sources combined:

- 2010 **census** statistics
- 2019 **PASO** presidential election
- 2015 **PASO** presidential election
- 2015 **presidential** election

Data is aggregated at "circuito", the lowest level at which electoral results are available. In Argentina, census and electoral geography are independent so I had to create a lookup file for correspondences between census tracks and electoral "circuitos". I did this by computing the area intersected between both sets of boundaries.

## The dataset

```{r, echo=FALSE}
d <- read_rds("arg_elec_censo_wide.RDS")
head(d, 5)
```


### Variables

```{r, echo=FALSE}
tibble(Variable = c("vi_cal_cons_", "vi_cal_servbas_", "vi_cal_mat_", 
                                 "vi_tipo_", "vi_nho_", "vi_urban_", 
                                 "vi_tipo_part_", "vi_tipo_ocupa_", "ho_nbi_", 
                                 "ho_suelo_", "ho_techo_", "ho_rev_int_", 
                                 "ho_agua_", "ho_agua_beber_", "ho_aseo_", 
                                 "ho_cadena_", "ho_desague_", "ho_combus_", 
                                 "ho_refri_", "ho_compu_", 
                                 "ho_celu_", "ho_fijo_", "ho_hacinam_", 
                                 "ho_nhogar_", "ho_prop_", "ho_npers_", 
                                 "per_siteco_", "per_edad_gru_", 
                                 "per_edad_quin_", "per_rela_jefe_", 
                                 "per_sexo_", "per_inmig_", 
                                 "per_leer_", "per_escuela_", "per_educa_", 
                                 "per_educa_completo_", "per_compu_"),
                                Summary = c("Calidad constructiva de la vivienda",
                                "Calidad de Conexiones a Servicios Básicos",
                                "Calidad de los materiales",
                                "Tipo de vivienda agrupado",
                                "Cantidad de Hogares en la Vivienda",
                                "Area Urbano - Rural",
                                "Tipo de vivienda particular",
                                "Condición de ocupación",
                                "Al menos un indicador NBI",
                                "Material predominante de los pisos",
                                "Material predominante de la cubierta exterior del techo",
                                "Revestimiento interior o cielorraso del techo",
                                "Tenencia de agua",
                                "Procedencia del agua para beber y cocinar",
                                "Tiene baño / letrina",
                                "Tiene botón, cadena, mochila para limpieza del inodoro",
                                "Desagüe del inodoro",
                                "Baño / letrina de uso exclusivo",
                                "Combustible usado principalmente para cocinar",
                                "Heladera",
                                "Computadora",
                                "Teléfono celular",
                                "Teléfono de línea",
                                "Hacinamiento",
                                "Régimen de tenencia",
                                "Total de Personas en el Hogar",
                                "Condición de actividad",
                                "Edad en grandes grupos",
                                "Edades quinquenales",
                                "Relación o parentesco con el jefe(a) del hogar",
                                "Sexo",
                                "En que país nació",
                                "Sabe leer y escribir",
                                "Condición de asistencia escolar",
                                "Nivel educativo que cursa o cursó",
                                "Completó el nivel",
                                "Utiliza computadora")) %>% 
  kableExtra::kable()

```


## How it was built


 