---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(tidyverse)
```

# Dataset: 2019 Argentine General Election

The resulting dataset is availabel in `csv` (for excel) and `RDS` (for R) formats:

- `arg_elec_censo_wide.csv`
- `arg_elec_censo_wide.RDS`

This project aims to create a dataset combining census statistics and electoral results. These are the data sources combined:

- 2010 **census** statistics
- 2019 **PASO** presidential election
- 2015 **PASO** presidential election
- 2015 **presidential** election

Data is aggregated at "circuito", the lowest level at which electoral results are available. In Argentina, census and electoral geography are independent so I had to create a lookup file for correspondences between census tracks and electoral "circuitos". I did this by computing the area intersected between both set of boundaries.

## The dataset

```{r}
plot(mtcars)
```


### Variables

## How it was built


 